---
title: "Homework-1"
author: Andy Mark 
output:
  html_document: default
---

##Challange 1
```{r, echo=TRUE}
v <- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed"
```

```{r}
u <- gsub("[[:punct:]]","",v)
u
```
this is what I did to get rid of the puncuations because if they are in this it wont work
```{r}
library(stringr)
u2 <- str_split(u, " ", n=22, simplify = FALSE) 
u2
```
This is what I used to sapersate everything out and split it into different parts
```{r}
u3 <- unlist(u2)
u3
```
This was used so the project wouldnt be in a list and I could select the individual stuff
```{r}
u4 <- u3[seq(from = 1, to = 22, by = 3)] 
u4
```
This was a way to select every 3rd word after the list was unlisted
##Challenge 2
```{r}
Platyrrhini <- list("Cebidae", "Atelidae", "Pitheciidae")
```
I used the list comand to do this park
```{r}
Catarrhini <- list("Cercopithecidae", "Hylobatidae", "Hominidae")
```

```{r}
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini","Catarrhini")
```
I used names comand so I help generat my list
```{r}
Tarsioidea <-list("Tarsiidae")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
```

```{r}
Lorisoidea <- list("Lorisidae", "Galagidae")
Lemuroidea <- list("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Strepsirhini <- list(Lorisoidea, Lemuroidea)
names(Strepsirhini) <- list("Lorisoidea", "Lemuroidea")
```

```{r}
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
```

```{r}
x <-list(Primates)
x
Primates
```